---
title: "Preprocessing Notebook"
output: html_document
---

```{r setup, include=FALSE}
# Install and load required packages
# install.packages("tidyverse")
# install.packages("lubridate")
# install.packages("config")
# install.packages("repr")
library(tidyverse)
library(dplyr)
library(stringr)
library(lubridate)
library(config)
library(digest)
library(glue)
library(repr)
library(tibble)
```


```{r}
# Set options for data frame display
options(tibble.width = Inf)
options(tibble.print_max = 50)
```

# Functions

```{r}
convert_to_snake_case <- function(col_name) {
  # Remove '__c' from the column names
  col_name <- gsub('__c', '', col_name)
  
  # Replace periods with underscores
  col_name <- gsub('\\.', '_', col_name)
  
  # Convert camel case to snake case
  # Handle the case where a lowercase letter or digit is followed by an uppercase letter
  col_name <- gsub('([a-z0-9])([A-Z])', '\\1_\\2', col_name)
  
  # Convert the entire string to lowercase
  col_name <- tolower(col_name)
  
  # Replace multiple underscores with a single underscore
  col_name <- gsub('_+', '_', col_name)
  
  return(col_name)
}
```

```{r}
# Define a function to convert entries to datetime
convert_to_datetime <- function(entry) {
  # Convert a given entry into a datetime object using R's as.POSIXct function.
  # Args:
  #   entry (character): The entry to convert to datetime.
  # Returns:
  #   POSIXct: Returns a POSIXct object if conversion is successful, otherwise NA.
  
  tryCatch({
    # Try to parse as a full date
    as.POSIXct(entry, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")
  }, error = function(e) {
    # Check if it's a four-digit number (likely representing a year)
    if (grepl("^\\d{4}$", entry)) {
      as.POSIXct(paste0(entry, "-01-01"), format = "%Y-%m-%d", tz = "UTC")
    } else {
      # If it's neither a full date nor a valid year, return NA or handle as needed
      NA
    }
  })
}
```

```{r}
# Function to check if the given value is a valid Roman numeral
is_roman_numeral <- function(value) {
  # Define a regular expression to match Roman numerals
  roman_pattern <- "^M{0,3}(CM|CD|D?C{0,3})(XC|XL|L?X{0,3})(IX|IV|V?I{0,3})$"
  
  # Check if the value matches the Roman numeral pattern
  return(grepl(roman_pattern, value))
}

# Function to check if the given value has a digit
has_digit <- function(value) {
  return(grepl("\\d", as.character(value)))
}

# Function to check if the given value is a Roman numeral or contains a digit
roman_or_numeral <- function(value) {
  if (is_roman_numeral(value) || has_digit(value)) {
    return(TRUE)
  } else {
    return(FALSE)
  }
}
```


```{r}
# Function to find elements in lst1 that are not in lst2
intersection_out <- function(lst1, lst2) {
  lst3 <- lst1[!(lst1 %in% lst2)]
  return(lst3)
}

# Function to find elements in lst1 that are also in lst2
intersection_in <- function(lst1, lst2) {
  lst3 <- lst1[lst1 %in% lst2]
  return(lst3)
}
```


```{r}
# Function to check if a given string `cell` meets specific inclusion and exclusion criteria
# 
# Args:
#   cell (character): The string to check.
#   included_and (character vector, optional): List of keywords; cell must include all of these (case insensitive).
#   included_or (character vector, optional): List of keywords; cell must include at least one of these (case insensitive).
#   excluded_and (character vector, optional): List of keywords; cell must not include any of these (case insensitive).
#   excluded_or (character vector, optional): List of keywords; cell must not include at least one of these (case insensitive).
# 
# Returns:
#   logical: TRUE if `cell` meets all specified criteria, FALSE otherwise.
 
generalized_contains <- function(cell, included_and=NULL, included_or=NULL, excluded_and=NULL, excluded_or=NULL) {
  if (!is.character(cell)) {
    return(FALSE)  # Return FALSE if `cell` is not a string
  }
  
  cell_lower <- tolower(cell)  # Convert `cell` to lowercase
  
  # Check included_and condition
  if (!is.null(included_and)) {
    if (!all(sapply(included_and, function(keyword) grepl(keyword, cell_lower)))) {
      return(FALSE)  # Return FALSE if `cell_lower` does not contain all keywords in `included_and`
    }
  }
  
  # Check included_or condition
  if (!is.null(included_or)) {
    if (!any(sapply(included_or, function(keyword) grepl(keyword, cell_lower)))) {
      return(FALSE)  # Return FALSE if `cell_lower` does not contain any keyword in `included_or`
    }
  }
  
  # Check excluded_and condition
  if (!is.null(excluded_and)) {
    if (any(sapply(excluded_and, function(keyword) grepl(keyword, cell_lower)))) {
      return(FALSE)  # Return FALSE if `cell_lower` contains any keyword in `excluded_and`
    }
  }
  
  # Check excluded_or condition
  if (!is.null(excluded_or)) {
    if (any(sapply(excluded_or, function(keyword) grepl(keyword, cell_lower)))) {
      return(FALSE)  # Return FALSE if `cell_lower` contains any keyword in `excluded_or`
    }
  }
  
  return(TRUE)  # Return TRUE if all conditions are satisfied
}
```

```{r}
# Function to pick a value from either col1 or col2 of a given row based on priority rules
# 
# Args:
#   row (data.frame row): The row (data.frame row) from which to pick values.
#   col1 (character): The name of the first column to consider.
#   col2 (character): The name of the second column to consider.
# 
# Returns:
#   object: The value from col1 or col2 based on the priority rules:
#       - If both values are NA, returns NA.
#       - If only one value is NA, returns the non-NA value.
#       - If both values are equal and not NA, returns that value.
#       - Otherwise, returns NA and prints the conflicting values (for debugging).

pick_col <- function(row, col1, col2) {
  x <- row[[col1]]
  y <- row[[col2]]
  
  if (is.na(x) && is.na(y)) {
    return(NA)  # Return NA if both values are NA
  } else if (is.na(x)) {
    return(y)   # Return y if x is NA
  } else if (is.na(y)) {
    return(x)   # Return x if y is NA
  } else if (x == y) {
    return(x)   # Return x (or y, since x == y) if both are equal and not NA
  } else {
    cat(paste(x, y, sep = " "), "\n")  # Print conflicting values for debugging
    return(NA)  # Return NA for conflicting values
  }
}
```

```{r}
# Function to rename the '_merge' column in the merged dataframe to a source indicator column,
# and map its values to more descriptive labels based on merge sources.
# 
# Args:
#   merged_df (data.frame): The merged dataframe resulting from a merge operation.
#   left_source (character): The label for the left dataframe source.
#   right_source (character): The label for the right dataframe source.
# 
# Returns:
#   data.frame: The merged dataframe `merged_df` with the '_merge' column renamed to indicate source,
#               and its values mapped to descriptive labels based on merge sources.

df_merge_source <- function(merged_df, left_source, right_source) {
  # Rename the '_merge' column to 'source'
  new_col <- "df_source"
  while (new_col %in% names(merged_df)) {
    i <- 1
    new_col <- paste0("df_source_", i)
    i <- i + 1
  }
  
  names(merged_df)[names(merged_df) == "_merge"] <- new_col
  
  # Map the source column to more descriptive labels
  source_mapping <- list(
    'left_only' = left_source,
    'right_only' = right_source,
    'both' = paste0(left_source, "/", right_source)
  )
  
  merged_df[[new_col]] <- factor(merged_df[[new_col]], levels = names(source_mapping))
  merged_df[[new_col]] <- factor(merged_df[[new_col]], labels = source_mapping)
  
  return(merged_df)
}
```

```{r}
# Function to remove dollar signs ('$') and commas (',') from a given string representation of a number
# 
# Args:
#   cell (character or any): The string or value from which to remove dollar signs and commas.
# 
# Returns:
#   character or any: The modified string with dollar signs and commas removed, or the original value if not a string.

remove_dollar_sign_and_comma <- function(cell) {
  if (is.character(cell)) {
    cell <- gsub("\\$|,", "", cell)  # Remove dollar signs ('$') and commas (',')
  }
  return(cell)
}
```

```{r}
# Function to save a data frame to a CSV file with a specified file name format and path
# 
# Args:
#   df (data.frame): The data frame to save.
#   file_prefix (character, optional): The prefix for the CSV file name. Default is "constituents_cleaned".
#   version (character, optional): The version identifier for the CSV file name. Default is "v1".
# 
# Returns:
#   NULL

save_file <- function(df, file_prefix = "constituents_cleaned", version = "v1") {
  # Check if "Unique Donor ID" column exists and drop rows with NA values in that column
  if ("Unique Donor ID" %in% names(df)) {
    df <- df[!is.na(df[["Unique Donor ID"]]), ]
  }
  
  # Construct file name based on file_prefix and version
  file_name <- paste0(file_prefix, "_", version, ".csv")
  
  # Define file path components (replace with actual paths as needed)
  file_path <- "/path/to/your/file"  # Replace with actual file path
  clients <- "your_clients_folder"   # Replace with actual clients folder
  subdir <- "your_subdirectory"      # Replace with actual subdirectory
  
  # Create directory structure if it doesn't exist
  dir.create(file.path(file_path, "Cleaning"), showWarnings = FALSE, recursive = TRUE)
  
  # Save data frame to CSV file
  write.csv(df, file.path(file_path, "Cleaning", file_name), row.names = FALSE)
}
```

# Variables

```{r}
# user <- "Rmittal"
# file_path <- sprintf("C:\\Users\\%s\\CCS\\Internal - Analytics - Shared Drive\\1. Shared Drive\\Clients", user)
# clients = "The Conservation Fund"
# subdir = "Raw Client Data"

file_path <- "C:/Users/Lvu/Internal - Analytics/"

save_constit_before_mapping <- "constituents_before_mapping"
save_constit_after_mapping <- "constituents_preprocessed"
save_gifts_after_mapping <- "gifts_preprocessed"

mapper <- "data_mapping_template.csv"
```

# Gifts Data

```{r}
file_name <- "gifts_raw_data.csv"
file <- file.path(file_path, file_name)
df_gd <- read.csv(file, encoding="ISO-8859-1")
```

```{r}
# when the gift_type is "write_off", the amount needs to be made negative
save_file(df_gd, save_gifts_after_mapping)
```

# Constituents Data

```{r}
file_name <- "constituents_raw_data.csv"
file <- file.path(file_path, file_name)
df_cd <- read.csv(file, encoding="ISO-8859-1")
```

## Run the python script function

```{r}
# Read the sample data 
# df_cd_sample <- read.csv("./constituents_raw_data.csv", encoding="ISO-8859-1")
```

```{r}
# # install.packages("renv")
# library(renv)
# 
# ## Initialize renv
# renv::init()
# 
# ## Save the R packages used
# renv::snapshot()
# 
# # renv::dependencies()
# 
# # install.packages("reticulate")
# library(reticulate)
# 
# ## Specify the path to the virtual environment
# virtualenv_path <- "./.py3117_preprocessing"
# use_virtualenv(virtualenv_path, required = TRUE)
# 
# ## Source the Python script
# source_python("./data_profiling.py")
# 
# ## Define the file path to be passed to the Python function
# file_path <- "./constituents_sample_data.csv"
# 
# # Call the Python function with the specified file path
# py$generate_profile_report(file_path)
```

```{r}
install.packages("renv")

## Restore the R environment
renv::restore()

library(reticulate)

## Specify the path to the virtual environment
venv_path <- file.path(getwd(), ".venv")
use_virtualenv(venv_path, required = TRUE)

## Source the Python script
source_python("./data_profiling.py")

## Define the file path to be passed to the Python function
file_path <- "./constituents_sample_data.csv"

# Call the Python function with the specified file path
py$generate_profile_report(file_path)
```


# Formatting

**Remove dollar sign and comma**

```{r}
# Remove dollar sign and comma
df_cd <- df_cd %>% mutate(across(everything(), remove_dollar_sign_and_comma))

# Convert giving columns to numeric
givings_columns <- grep("giving", tolower(names(df_cd)), value = TRUE)
df_cd <- df_cd %>% mutate(across(all_of(givings_columns), as.numeric))
```

# Renaming

## key_indicator

```{r}
df_cd["key_indicator"].value_counts()
```

## is_individual

```{r}
df_cd <- df_cd %>% mutate(is_individual = ifelse(key_indicator == "I", TRUE, FALSE))
```

## is_deceased

```{r}
df_cd <- df_cd %>% mutate(is_deceased = ifelse(Deceased == "Yes", TRUE, FALSE))
```

```{r}
# Apply generalized_contains for current_trustee_indicator
columns_constituent <- grep("constituent", tolower(names(df_cd)), value = TRUE)
df_cd <- df_cd %>% mutate(current_trustee_indicator = pmap_lgl(df_cd[columns_constituent], generalized_contains, included_and = c("board", "member")))

# Apply generalized_contains for past_trustee_indicator
df_cd <- df_cd %>% mutate(past_trustee_indicator = pmap_lgl(df_cd[columns_constituent], generalized_contains, included_and = c("board", "member"), included_or = c("past", "former")))
```

## head_of_household and household_id

```{r}
# Function to determine index of row with max "Total Lifetime Giving" or default to first row
get_max_index <- function(group) {
  if ("Total Lifetime Giving" %in% names(group)) {
    if (max(group$`Total Lifetime Giving`, na.rm = TRUE) > 0) {
      return(which.max(group$`Total Lifetime Giving`))
    }
  }
  return(1)
}
```

```{r}
df_cdi <- df_cd %>% filter(!is_deceased & is_individual) %>% mutate(head_of_household = TRUE)
```

```{r}
# Drop rows where both Addr1 and Addr2 are NaN
df_cdi <- df_cdi %>% drop_na(Address_1, Address_2, how = "all")

# Fill NaNs with a placeholder value (e.g., 'missing')
df_cdi <- df_cdi %>% replace_na(list(Address_1 = "missing", Address_2 = "missing", City = "missing", State = "missing", Zip = "missing"))

# Filter rows to ensure there's something numeric in at least one of Addr1 or Addr2
df_cdi <- df_cdi %>% filter(apply(df_cdi, 1, function(row) roman_or_numeral(row["Address_1"]) | roman_or_numeral(row["Address_2"])))

df_cdi_multiple <- df_cdi %>% group_by(Address_1, Address_2, City, State, Zip) %>% filter(n() > 1) %>% arrange(Address_1, Address_2, City, State, Zip)

# Identify index of rows with max "Total Lifetime Giving" or default to first row
idx_max_lifetime_giving <- df_cdi_multiple %>% group_by(Address_1, Address_2, City, State, Zip) %>% summarize(idx = get_max_index(cur_data()), .groups = "drop")

# Set "head_of_household" to False for all entries in subgroups with multiple entries
df_cdi <- df_cdi %>% mutate(head_of_household = ifelse(row_number() %in% idx_max_lifetime_giving$idx, TRUE, FALSE))

# Assign unique household_id to each subgroup
df_cdi_multiple <- df_cdi_multiple %>% group_by(Address_1, Address_2, City, State, Zip) %>% mutate(household_id = row_number())

# Merge the household_id back into the original df_cdi
df_cdi <- df_cdi %>% left_join(df_cdi_multiple %>% select(Unique_Donor_ID, household_id), by = "Unique Donor ID") %>% replace_na(list(household_id = 0))

# Merge the head_of_household and household_id into df_cd
df_cd <- df_cd %>% left_join(df_cdi %>% select(Unique_Donor_ID, head_of_household, household_id), by = "Unique Donor ID")
```

## is_assigned

```{r}
# Get column names for solicitor types and names
columns_solicitor_type <- grep("solicitor type", tolower(names(df_cd)), value = TRUE)
columns_solicitor_name <- grep("solicitor name", tolower(names(df_cd)), value = TRUE)

# Initialize a column to store the final result
df_cd <- df_cd %>% mutate(is_assigned = FALSE)

# Loop through each pair of columns using zip
for (i in 1:length(columns_solicitor_type)) {
  solicitor_type_col <- columns_solicitor_type[i]
  solicitor_name_col <- columns_solicitor_name[i]

  df_cd <- df_cd %>% mutate(
    is_assigned_1 = mapply(generalized_contains, df_cd[[solicitor_type_col]], MoreArgs = list(included_or = c("solicitor", "prospect manager"), excluded_or = c("2"))),
    is_assigned_2 = mapply(generalized_contains, df_cd[[solicitor_name_col]], MoreArgs = list(excluded_and = c("president", "lawrence a. selzer")))
  )
  
  df_cd <- df_cd %>% mutate(is_assigned = is_assigned | (is_assigned_1 & is_assigned_2))
}

# Drop intermediate columns
df_cd <- df_cd %>% select(-c(is_assigned_1, is_assigned_2))
```

## assigned_manager

```{r}
# Define conditions
conditions <- list(
  df_cd$is_assigned == TRUE & !is.na(df_cd$Solicitor_Name_1) & !grepl("president|lawrence a. selzer", df_cd$Solicitor_Name_1, ignore.case = TRUE),
  df_cd$is_assigned == TRUE & !is.na(df_cd$Solicitor_Name_2) & !grepl("president|lawrence a. selzer", df_cd$Solicitor_Name_2, ignore.case = TRUE),
  df_cd$is_assigned == TRUE & !is.na(df_cd$Solicitor_Name_3) & !grepl("president|lawrence a. selzer", df_cd$Solicitor_Name_3, ignore.case = TRUE),
  df_cd$is_assigned == TRUE & !is.na(df_cd$Solicitor_Name_4) & !grepl("president|lawrence a. selzer", df_cd$Solicitor_Name_4, ignore.case = TRUE),
  df_cd$is_assigned == TRUE & !is.na(df_cd$Solicitor_Name_5) & !grepl("president|lawrence a. selzer", df_cd$Solicitor_Name_5, ignore.case = TRUE),
  df_cd$is_assigned == TRUE & !is.na(df_cd$Solicitor_Name_6) & !grepl("president|lawrence a. selzer", df_cd$Solicitor_Name_6, ignore.case = TRUE)
)

# Define choices corresponding to the conditions
choices <- list(
  df_cd$Solicitor_Name_1,
  df_cd$Solicitor_Name_2,
  df_cd$Solicitor_Name_3,
  df_cd$Solicitor_Name_4,
  df_cd$Solicitor_Name_5,
  df_cd$Solicitor_Name_6
)

# Use case_when to create the 'assigned_manager' column
df_cd <- df_cd %>% mutate(assigned_manager = case_when(
  conditions[[1]] ~ choices[[1]],
  conditions[[2]] ~ choices[[2]],
  conditions[[3]] ~ choices[[3]],
  conditions[[4]] ~ choices[[4]],
  conditions[[5]] ~ choices[[5]],
  conditions[[6]] ~ choices[[6]],
  TRUE ~ NA_character_
))
```

## solicit_codes

```{r}
if ("solicit_codes" %in% names(df_cd)) {
  df_cd <- df_cd %>% select(-solicit_codes)
}
columns_solicit_codes <- grep("solicit", tolower(names(df_cd)), value = TRUE)
df_cd <- df_cd %>% mutate(solicit_codes = rowSums(!is.na(select(df_cd, all_of(columns_solicit_codes)))) > 0)
df_cd$solicit_codes <- as.integer(df_cd$solicit_codes)
```

## marital_status

```{r}
columns_spouse <- grep("spouse", tolower(names(df_cd)), value = TRUE, invert = TRUE)
df_cd <- df_cd %>% mutate(marital_status = ifelse(rowSums(!is.na(select(df_cd, all_of(columns_spouse)))) > 0, "married", NA))
df_cd <- df_cd %>% mutate(marital_status = ifelse(`Spouse deceased`, "widow", marital_status))
```

## five_year_giving

```{r}
df_cd <- df_cd %>% mutate(five_year_giving = `2024 Giving Total` + `2023 Giving Total` + `2022 Giving Total` + `2021 Giving Total` + `2020 Giving Total` + `2019 Giving Total`)
```

```{r}
df_cd <- df_cd %>% mutate(major_donor_model_score = 0, loyalty_model_score = 0, n_years_giving_of_ten = NA)
```

## planned_gift_commitment

```{r}
columns_planned <- grep("planned", tolower(names(df_cd)), value = TRUE)
df_cd <- df_cd %>% mutate(planned_gift_commitment = ifelse(rowSums(!is.na(select(df_cd, all_of(columns_planned)))) > 0, 1, 0))
```

## Address

```{r}
df_cd <- df_cd %>% mutate(business_address = preferred_address_type == "Business")
df_cd <- df_cd %>% mutate(seasonal_address = grepl("summer|winter|alternate", preferred_address_type, ignore.case = TRUE))
```

## Phone

```{r}
df_cd <- df_cd %>% mutate(home_phone = ifelse(`Phone Type` == "Home", `Phone Number`, NA))
df_cd <- df_cd %>% mutate(home_phone = ifelse((`Phone Type_1` == "Home") & is.na(home_phone), `Phone Number_1`, home_phone))

df_cd <- df_cd %>% mutate(cell_phone = ifelse(`Phone Type` == "Cell", `Phone Number`, NA))
df_cd <- df_cd %>% mutate(cell_phone = ifelse((`Phone Type_1` == "Cell") & is.na(cell_phone), `Phone Number_1`, cell_phone))
```

## Email

```{r}
df_cd <- df_cd %>% mutate(personal_email = coalesce(`Email`, `Email_1`, `Email_2`, `Email_3`))
```

## number_of_events_attended

```{r}
df_cd <- df_cd %>% mutate(number_of_special_events_attended = rowSums(!is.na(select(df_cd, Events:Events_5))))
```

## total_notes

```{r}
df_cd <- df_cd %>% mutate(Total_Notes = coalesce(`Total_Notes`, 0))
df_cd <- df_cd %>% mutate(`Total Notes` = coalesce(`Total Notes`, 0))
df_cd <- df_cd %>% mutate(total_notes = `Total_Notes` + `Total Notes`)
```

## Loyalty

```{r}
columns_yearly_giving <- c("2023 Total Giving", "2022 Total Giving", "2021 Total Giving", "2020 Total Giving", "2019 Total Giving", "2018 Total Giving", "2017 Total Giving", "2016 Total Giving", "2015 Total Giving", "2014 Total Giving")
```


```{r}
# Function to determine the first year a gift was made
first_gift_year <- function(row) {
  first_gift_year <- NA
  for (i in seq_along(columns_yearly_giving)) {
    if (row[[columns_yearly_giving[i]]] > 0) {
      first_gift_year <- current_year - i
      break
    }
  }
  return(first_gift_year)
}

# Function to calculate the number of years gifts were made
years_gifts_made <- function(row) {
  return(sum(row[columns_yearly_giving] > 0))
}

# Function to calculate loyalty
calculate_loyalty <- function(row) {
  if (!is.na(row[["first_gift_year"]])) {
    return(row[["number_of_years_gifts_were_made"]] / (current_year - row[["first_gift_year"]]))
  }
  return(0)
}
```

```{r}
# Get the current year
current_year <- year(Sys.Date())

df_cd <- df_cd %>% rowwise() %>% mutate(first_gift_year = first_gift_year(cur_data()), number_of_years_gifts_were_made = years_gifts_made(cur_data()), loyalty = calculate_loyalty(cur_data()))
```

**Save file before applying mapper**

```{r}
save_file(df_cd, save_constit_before_mapping, "v1")
```

# Mapper

**ADD A CHECK TO ENSURE NO FIELDS ARE DUPLICATED**

```{r}
mapping <- read_csv(mapper)
column_mapping <- mapping %>% filter(file_columns != "not_found") %>% select(file_columns, expected_columns) %>% deframe()
df_final <- df_cd %>% rename(!!!column_mapping)
df_final <- df_final %>% select(all_of(column_mapping))
```

## Datatypes

### Age

```{r}
# Convert age column to datetime
df_final <- df_final %>% mutate(age = as_date(convert_to_datetime(age)))
```

## Save the final preprocessed-file

```{r}
save_file(df_final, save_constit_after_mapping, "v1")
```

### Correlation Plots with Total Lifetime Giving

```{r}
library(ggplot2)

# Drop rows with NaNs in these columns
df_cleaned <- df_cdi_multiple %>% drop_na(`Total Lifetime Giving`, `Total Actions`)

ggplot(df_cleaned, aes(x = log(`Total Lifetime Giving`), y = `Total Actions`)) +
  geom_point() +
  labs(title = "Scatter Plot of Total Lifetime Giving vs. Total Actions",
       x = "Total Lifetime Giving (log scale)",
       y = "Total Actions") +
  theme_minimal()

df_cleaned <- df_cdi_multiple %>% drop_na(`Total Lifetime Giving`, `Pledged Planned Gift`)

ggplot(df_cleaned, aes(x = log(`Total Lifetime Giving`), y = `Pledged Planned Gift`)) +
  geom_point() +
  labs(title = "Scatter Plot of Total Lifetime Giving vs. Pledged Planned Gift",
       x = "Total Lifetime Giving (log scale)",
       y = "Pledged Planned Gift") +
  theme_minimal()
```